Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-02-28 src/tex/ms.tex
Update ms.tex
GW200129 plot

\begin{figure}
    \script{corner_Gaussian.py}
    \includegraphics[width=\columnwidth]{figures/corner_Gaussian.pdf}
    \caption{
        The posterior of $\mu$ and $\sigma$ of the population distribution of $\kappa$.
        2D contour plot shows $39.35\%$ and $90\%$ confidence level.
        The orange line represents the median of $\mu$ and $\sigma$.
        The plot shows that the population constraint on $\kappa$ is consistent with GR.
    }
    \label{fig:corner_Gaussian}
\end{figure}

@@

\subsection{Constaint on $\kappa$}
% Constraint on $\kappa$
In Fig.~\ref{fig:posterior_kappa}, we show both the restricted posterior of $\kappa$ and the generic posterior of $\kappa$.
The restricted posterior is calculated by Eq.~\eqref{eq:restricted_posterior} with the assumption that $\kappa$ is a single value constant.
The generic posterior is calculated by Eq.~\eqref{eq:generic_posterior} with the assumption that $\kappa$ is a true value drawn from a Gaussian distribution.
The median of the restricted posterior within $90\%$ confidence interval is \variable{output/restricted_kappa_median.txt}.
The median of the generic posterior within $90\%$ confidence interval is \variable{output/generic_kappa_median.txt}.
Note that the result is consistent with GR when $\kappa=0$.
% talk about what events pull sigma in figure 2

@@

\begin{figure}
    \script{corner_GW150914.py}
    \includegraphics[width=\columnwidth]{figures/corner_GW150914.pdf}
    \caption{
        The posterior of $\kappa$, luminosity distance $d_L$ and $\cos{\iota}$ for GW150914.
        Colors in the plot represent the \ac{PE} result with GR done by LVK without cosmological reweighing \citep{GWTC-2.1, GWTC-3, GWTC-2.1_dataset, GWTC-3_dataset}, the \ac{PE} results done by us with both frequency-independent and dependent birefringence respectively.
        2D contour plot shows $39.35\%$ and $90\%$ confidence level.
        Note that there is no posterior of $\kappa$ for the \ac{PE} result from LVK, as the LVK \ac{PE} is based on GR, which does not suggest GW amplitude birefringence.
        This plot shows that frequency-independent birefringence creates a degeneracy between $\kappa$ and $\iota$, while frequency-dependent birefringence can break it.
    }
    \label{fig:corner_GW150914}
\end{figure}

@@

\begin{figure}[h]
    \script{corner_GW190521.py}
    \includegraphics[width=\columnwidth]{figures/corner_GW190521.pdf}
    \caption{
        The posterior of $\kappa$, luminosity distance $d_L$ and $\cos{\iota}$ for GW190521.
        Colors in the plot are the \ac{PE} result with GR done by LVK without cosmological reweighing \citep{GWTC-2.1, GWTC-3, GWTC-2.1_dataset, GWTC-3_dataset} and the \ac{PE} result done by us with the frequency-dependent birefringence.
        2D contour plot shows $39.35\%$ and $90\%$ confidence level.
        This plot shows that frequency-dependent birefringence cannot break the degeneracy between $\kappa$ and $\iota$.
    }
    \label{fig:corner_GW190521}
\end{figure}

@@

\begin{figure}
    \script{corner_GW200129.py}
    \includegraphics[width=\columnwidth]{figures/corner_GW200129.pdf}
    \caption{
        The posterior of $\kappa$, luminosity distance $d_L$ and $\cos{\iota}$ for GW200129.
        Colors in the plot are the \ac{PE} result with GR done by LVK without cosmological reweighing \citep{GWTC-2.1, GWTC-3, GWTC-2.1_dataset, GWTC-3_dataset} and the \ac{PE} result done by us with and without Virgo data.
        2D contour plot shows $39.35\%$ and $90\%$ confidence level.
        This plot shows that Virgo data may contain a glitch, which affects the \ac{PE} result.
    }
    \label{fig:corner_GW200129}
\end{figure}

>>>>

\begin{figure}
    \script{corner_Gaussian.py}
    \includegraphics[width=\columnwidth]{figures/corner_Gaussian.pdf}
    \caption{
        The posterior of the $\kappa$ population hyperparameters $\mu$ and $\sigma$, including (blue) and excluding (orange) GW200129 from the collection of events.
        The 2D contours correspond to the $39.35\%$ and $90\%$ credible levels.
        The plot shows that the population constraint on $\kappa$ is consistent with no birefringence ($\mu=\sigma=0$) at the 90\% credible level.
    }
    \label{fig:corner_Gaussian}
\end{figure}

@@

\subsection{Constaint on $\kappa$}
% Constraint on $\kappa$
In Fig.~\ref{fig:posterior_kappa}, we show both the restricted posterior of $\kappa$ and the generic posterior of $\kappa$.
The restricted posterior is calculated by Eq.~\eqref{eq:restricted_posterior} with the assumption that $\kappa$ is a single value constant.
The generic posterior is calculated by Eq.~\eqref{eq:generic_posterior} with the assumption that $\kappa$ is a true value drawn from a Gaussian distribution.
The median of the restricted posterior within $90\%$ confidence interval is \variable{output/restricted_kappa_median.txt}.
The median of the generic posterior within $90\%$ confidence interval is \variable{output/generic_kappa_median.txt}.
Note that the result is consistent with GR when $\kappa=0$.

@@

\begin{figure}
    \script{corner_GW150914.py}
    \includegraphics[width=\columnwidth]{figures/corner_GW150914.pdf}
    \caption{
        The posterior of $\kappa$, luminosity distance $d_L$ and $\cos{\iota}$ for GW150914.
        Colors in the plot represent the \ac{PE} result with GR done by LVK without cosmological reweighing \citep{GWTC-2.1, GWTC-3, GWTC-2.1_dataset, GWTC-3_dataset}, the \ac{PE} results done by us with both frequency-independent and dependent birefringence respectively.
        The 2D contours correspond to the $39.35\%$ ($1\sigma$) and $90\%$ credible levels.
        Note that there is no posterior of $\kappa$ for the \ac{PE} result from LVK, as the LVK \ac{PE} is based on GR, which does not suggest GW amplitude birefringence.
        This plot shows that frequency-independent birefringence creates a degeneracy between $\kappa$ and $\iota$, while frequency-dependent birefringence can break it.
    }
    \label{fig:corner_GW150914}
\end{figure}

@@

\begin{figure}[h]
    \script{corner_GW190521.py}
    \includegraphics[width=\columnwidth]{figures/corner_GW190521.pdf}
    \caption{
        The posterior of $\kappa$, luminosity distance $d_L$ and $\cos{\iota}$ for GW190521.
        Colors in the plot are the \ac{PE} result with GR done by LVK without cosmological reweighing \citep{GWTC-2.1, GWTC-3, GWTC-2.1_dataset, GWTC-3_dataset} and the \ac{PE} result done by us with the frequency-dependent birefringence.
        The 2D contours correspond to the $39.35\%$ ($1\sigma$) and $90\%$ credible levels.
        This plot shows that frequency-dependent birefringence cannot break the degeneracy between $\kappa$ and $\iota$.
    }
    \label{fig:corner_GW190521}
\end{figure}

@@

\begin{figure}
    \script{corner_GW200129.py}
    \includegraphics[width=\columnwidth]{figures/corner_GW200129.pdf}
    \caption{
        The posterior of $\kappa$, luminosity distance $d_L$ and $\cos{\iota}$ for GW200129.
        Colors in the plot are the \ac{PE} result with GR done by LVK without cosmological reweighing \citep{GWTC-2.1, GWTC-3, GWTC-2.1_dataset, GWTC-3_dataset} and the \ac{PE} result done by us with and without Virgo data.
        The 2D contours correspond to the $39.35\%$ ($1\sigma$) and $90\%$ credible levels.
        This plot shows that Virgo data may contain a glitch, which affects the \ac{PE} result.
    }
    \label{fig:corner_GW200129}
\end{figure}
